### 2025-08-22 getting-started.qmd
20250822 - drop stringi

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","patchwork","pROC",
     "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats","AICcmodavg",
     "rstan","brms","tidybayes","bbmle","fitdistrplus","sn","mclust",
     "magrittr","viridis","viridisLite","msir","plotly","webshot2","quantmod",
     "fPortfolio","NMOF","nFactors","xts","zoo","forecast","stringi",
     "parallelly","doParallel","missRanger","ggridges","powerjoin","caret",
     "LongituRF","gpboost","mgcv","rms","car","lavaan","lavaanPlot","lavaangui",
     "mice","miceadds","interactions","robustbase","ordinal","MASS",
     "data.table","future","future.apply","SimDesign","domir","GGally","Rglpk",
     "TTR"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

>>>>

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","patchwork","pROC",
     "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats","AICcmodavg",
     "rstan","brms","tidybayes","bbmle","fitdistrplus","sn","mclust",
     "magrittr","viridis","viridisLite","msir","plotly","webshot2","quantmod",
     "fPortfolio","NMOF","nFactors","xts","zoo","forecast","parallelly",
     "doParallel","missRanger","ggridges","powerjoin","caret","LongituRF",
     "gpboost","mgcv","rms","car","lavaan","lavaanPlot","lavaangui",
     "mice","miceadds","interactions","robustbase","ordinal","MASS",
     "data.table","future","future.apply","SimDesign","domir","GGally","Rglpk",
     "TTR"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

### 2025-08-22 index.qmd
20250822 - drop stringi

# Packages to drop: stringi (replace with stringr from tidyverse); caret (replace with tidymodels)

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "stringi", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "LongituRF", "gpboost", "cmdstanr", "mgcv", "rms", "car", "lavaan", 
  "lavaanPlot", "mice", "miceadds", "interactions", "robustbase", "ordinal", 
  "MASS", "data.table", "future", "future.apply", "SimDesign", "domir", 
  "GGally","Rglpk","TTR",
  "base","graphics","grDevices","grid","utils", # packages that are included with base R; get the full list with: rownames(installed.packages(priority="base"))
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS", "lavaangui", "dynamic" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)

>>>>

# Packages to drop: caret (replace with tidymodels)

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "LongituRF", "gpboost", "cmdstanr", "mgcv", "rms", "car", "lavaan", 
  "lavaanPlot", "mice", "miceadds", "interactions", "robustbase", "ordinal", 
  "MASS", "data.table", "future", "future.apply", "SimDesign", "domir", 
  "GGally","Rglpk","TTR",
  "base","graphics","grDevices","grid","utils", # packages that are included with base R; get the full list with: rownames(installed.packages(priority="base"))
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS", "lavaangui", "dynamic" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)
